timesliced_random_cell_selection

### 2018-11-05 src/timesliced_random_cell_selection.Rmd
can upload

2) reproject to a wgs

```{r}
sp_background <- spTransform(sp_background, CRS = "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")
plot(sp_background)
```
3) extract lonlat, add to dataframe

```{r}
head(sp_background)
```

save as csv

>>>>

2) reproject to a wgs (use an existing file as a mask)

```{r}
sp_background <- spTransform(sp_background, CRS = "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")
plot(sp_background)
```
3) extract lonlat, add to dataframe
save as csv

use the gebco raster as a mask?

```{r}
wgs84_mask <- gebco
plot(wgs84_mask)
```
